---
title: "Financial Crisis Stock Analysis"
format: revealjs
editor: visual
---

```{r output = FALSE}
library(quantmod)
library(lubridate)

start <- ymd("2008-01-01")
end <- ymd("2026-01-01")

getSymbols(c("SPY", "QQQ", "XLV", "XLF", "XLE", "VNQ"), src = "yahoo",
           from = start, to = end)

date_tib <- as_tibble(index(SPY)) |>
  rename(start_date = value)

qqq_tib <- as_tibble(QQQ)
spy_tib <- as_tibble(SPY)
xlv_tib <- as_tibble(XLV)
xlf_tib <- as_tibble(XLF)
xle_tib <- as_tibble(XLE)
vnq_tib <- as_tibble(VNQ)

all_stocks <- bind_cols(date_tib, qqq_tib, spy_tib, xlv_tib, xlf_tib, xle_tib, vnq_tib)


stocks_long <- all_stocks |>
  dplyr::select(start_date, QQQ.Adjusted, SPY.Adjusted, XLV.Adjusted, XLF.Adjusted,
                XLE.Adjusted, VNQ.Adjusted) |>
  pivot_longer(2:7, names_to = "Stock_Type", values_to = "Price") |>
  mutate(Stock_Type = fct_recode(Stock_Type,
                                 QQQ = "QQQ.Adjusted",
                                 sandp = "SPY.Adjusted",
                                 XLV = "XLV.Adjusted", 
                                 XLF = "XLF.Adjusted", 
                                 XLE = "XLE.Adjusted", 
                                 VNQ = "VNQ.Adjusted"
                                 ))

stocks_qqq <- stocks_long |> filter(Stock_Type == "QQQ")
stocks_spy <- stocks_long |> filter(Stock_Type == "sandp")
stocks_xlv <- stocks_long |> filter(Stock_Type == "XLV")
stocks_xlf <- stocks_long |> filter(Stock_Type == "XLF")
stocks_xle <- stocks_long |> filter(Stock_Type == "XLE")
stocks_vnq <- stocks_long |> filter(Stock_Type == "VNQ")


## looking at each ETF individually: 

ggplot(data = stocks_qqq, aes(x = start_date, y = Price)) +
  geom_line() +
  theme_minimal()

ggplot(data = stocks_spy, aes(x = start_date, y = Price)) +
  geom_line() +
  theme_minimal()

ggplot(data = stocks_xlv, aes(x = start_date, y = Price)) +
  geom_line() +
  theme_minimal()

ggplot(data = stocks_xlf, aes(x = start_date, y = Price)) +
  geom_line() +
  theme_minimal()

ggplot(data = stocks_xle, aes(x = start_date, y = Price)) +
  geom_line() +
  theme_minimal()

ggplot(data = stocks_vnq, aes(x = start_date, y = Price)) +
  geom_line() +
  theme_minimal()
```


## Data Introduction

  * Data taken from the quantmod() & lubridate()
  * Pulled from yahoofinance.com
  * Taking 6 ETF (Exchange Traded Funds) that track different industries
  * 'SFY' (Tracks the S&P500), 'QQQ' (Tracks Tech with the S&P), 'XLV' (Tracks 
  Health Care Sector), 'XLF' (Tracks Financial Sector), 'XLE' (Tracks Energy 
  Sector), 'VNQ' (Tracks Real Estate Sector)

## Question(s) of interest

  * What drives trading volume across different market sectors, and how does it 
  vary during periods of market stress?


## Price (2008 - 2026)

```{r}
ggplot(data = stocks_long, aes(x = start_date, y = Price)) +
  geom_line(aes(colour = Stock_Type)) +
  geom_area(aes(fill = Stock_Type), alpha = 0.2, position = "identity") +
  theme_minimal(base_size = 24) +
  scale_colour_viridis_d() +
  scale_fill_viridis_d() 
```

## Volume (2008 - 2026)

```{r output = FALSE}
stocks_volume <- all_stocks |>
  dplyr::select(start_date, QQQ.Volume, SPY.Volume, XLV.Volume, XLF.Volume,
                XLE.Volume, VNQ.Volume) |>
  pivot_longer(2:7, names_to = "Stock_Type", values_to = "Price") |>
  mutate(Stock_Type = fct_recode(Stock_Type,
                                 QQQ = "QQQ.Volume",
                                 sandp = "SPY.Volume",
                                 XLV = "XLV.Volume", 
                                 XLF = "XLF.Volume", 
                                 XLE = "XLE.Volume", 
                                 VNQ = "VNQ.Volume"
                                 ))

vol_qqq <- stocks_volume |> filter(Stock_Type == "QQQ")
vol_spy <- stocks_volume |> filter(Stock_Type == "sandp")
vol_xlv <- stocks_volume |> filter(Stock_Type == "XLV")
vol_xlf <- stocks_volume |> filter(Stock_Type == "XLF")
vol_xle <- stocks_volume |> filter(Stock_Type == "XLE")
vol_vnq <- stocks_volume |> filter(Stock_Type == "VNQ")

ggplot(data = stocks_qqq, aes(x = start_date, y = Price)) +
  geom_line() +
  theme_minimal()

ggplot(data = stocks_spy, aes(x = start_date, y = Price)) +
  geom_line() +
  theme_minimal()

ggplot(data = stocks_xlv, aes(x = start_date, y = Price)) +
  geom_line() +
  theme_minimal()

ggplot(data = stocks_xlf, aes(x = start_date, y = Price)) +
  geom_line() +
  theme_minimal()

ggplot(data = stocks_xle, aes(x = start_date, y = Price)) +
  geom_line() +
  theme_minimal()

ggplot(data = stocks_vnq, aes(x = start_date, y = Price)) +
  geom_line() +
  theme_minimal()
```


```{r}
ggplot(data = stocks_volume, aes(x = start_date, y = Price)) +
  geom_line(aes(colour = Stock_Type)) +
  geom_area(aes(fill = Stock_Type), alpha = 0.2, position = "identity") +
  theme_minimal(base_size = 24) +
  scale_colour_viridis_d() +
  scale_fill_viridis_d() 
```


## Volume in the 2008 Financial Crisis 

```{r output = FALSE}
start_vol_08 <- ymd("2008-01-01")
end_vol_11 <- ymd("2011-01-01")

getSymbols(c("SPY", "QQQ", "XLV", "XLF", "XLE", "VNQ"), src = "yahoo",
           from = start_vol_08, to = end_vol_11)

date_tib <- as_tibble(index(SPY)) |>
  rename(start_date = value)

qqq_tib <- as_tibble(QQQ)
spy_tib <- as_tibble(SPY)
xlv_tib <- as_tibble(XLV)
xlf_tib <- as_tibble(XLF)
xle_tib <- as_tibble(XLE)
vnq_tib <- as_tibble(VNQ)

all_stocks <- bind_cols(date_tib, qqq_tib, spy_tib, xlv_tib, xlf_tib, xle_tib, vnq_tib)

stocks_volume <- all_stocks |>
  dplyr::select(start_date, QQQ.Volume, SPY.Volume, XLV.Volume, XLF.Volume,
                XLE.Volume, VNQ.Volume) |>
  pivot_longer(2:7, names_to = "Stock_Type", values_to = "Price") |>
  mutate(Stock_Type = fct_recode(Stock_Type,
                                 QQQ = "QQQ.Volume",
                                 sandp = "SPY.Volume",
                                 XLV = "XLV.Volume", 
                                 XLF = "XLF.Volume", 
                                 XLE = "XLE.Volume", 
                                 VNQ = "VNQ.Volume"
                                 ))

vol_qqq <- stocks_volume |> filter(Stock_Type == "QQQ")
vol_spy <- stocks_volume |> filter(Stock_Type == "sandp")
vol_xlv <- stocks_volume |> filter(Stock_Type == "XLV")
vol_xlf <- stocks_volume |> filter(Stock_Type == "XLF")
vol_xle <- stocks_volume |> filter(Stock_Type == "XLE")
vol_vnq <- stocks_volume |> filter(Stock_Type == "VNQ")
```

```{r}
ggplot(data = stocks_volume, aes(x = start_date, y = Price)) +
  geom_line(aes(colour = Stock_Type)) +
  geom_area(aes(fill = Stock_Type), alpha = 0.2, position = "identity") +
  theme_minimal(base_size = 24) +
  scale_colour_viridis_d() +
  scale_fill_viridis_d()
```


## Volume in the 2020 Covid-19 Pandemic

```{r output = FALSE}
start_vol_2020 <- ymd("2020-01-01")
end_vol_2023 <- ymd("2023-01-01")

getSymbols(c("SPY", "QQQ", "XLV", "XLF", "XLE", "VNQ"), src = "yahoo",
           from = start_vol_2020, to = end_vol_2023)

date_tib <- as_tibble(index(SPY)) |>
  rename(start_date = value)

qqq_tib <- as_tibble(QQQ)
spy_tib <- as_tibble(SPY)
xlv_tib <- as_tibble(XLV)
xlf_tib <- as_tibble(XLF)
xle_tib <- as_tibble(XLE)
vnq_tib <- as_tibble(VNQ)

all_stocks <- bind_cols(date_tib, qqq_tib, spy_tib, xlv_tib, xlf_tib, xle_tib, vnq_tib)

stocks_volume <- all_stocks |>
  dplyr::select(start_date, QQQ.Volume, SPY.Volume, XLV.Volume, XLF.Volume,
                XLE.Volume, VNQ.Volume) |>
  pivot_longer(2:7, names_to = "Stock_Type", values_to = "Price") |>
  mutate(Stock_Type = fct_recode(Stock_Type,
                                 QQQ = "QQQ.Volume",
                                 sandp = "SPY.Volume",
                                 XLV = "XLV.Volume", 
                                 XLF = "XLF.Volume", 
                                 XLE = "XLE.Volume", 
                                 VNQ = "VNQ.Volume"
                                 ))

vol_qqq <- stocks_volume |> filter(Stock_Type == "QQQ")
vol_spy <- stocks_volume |> filter(Stock_Type == "sandp")
vol_xlv <- stocks_volume |> filter(Stock_Type == "XLV")
vol_xlf <- stocks_volume |> filter(Stock_Type == "XLF")
vol_xle <- stocks_volume |> filter(Stock_Type == "XLE")
vol_vnq <- stocks_volume |> filter(Stock_Type == "VNQ")
```

```{r}
ggplot(data = stocks_volume, aes(x = start_date, y = Price)) +
  geom_line(aes(colour = Stock_Type)) +
  geom_area(aes(fill = Stock_Type), alpha = 0.2, position = "identity") +
  theme_minimal(base_size = 24) +
  scale_colour_viridis_d() +
  scale_fill_viridis_d()
```

## Looking ahead: 

  * Model on predicting trading Volume (as a measure of volatility) 
  * Model Viz
  * Look into other measures of volatility

