---
title: "Trading Volatility and Volume During Financial Crises across industry ETFs"
author: "Alexa Santana"
format: 
  html:
    embed-resources: true
---

## Abstract:

This research project will look at exploring the relationship between the daily 
volatility in price in different industry's Exchange Traded Funds (ETFs), and 
how trading volume impacts it during financial crises. The data was taken from 
the 'quantmod()' package, which scrapes data Price and Volume data from 
YahooFinance. There is strong statistical evidence showing positive correlation 
between Volume traded and Daily Price changes in an ETF. This conclusion was 
further explored through visualizations of Volume during financial crises. 


## Introduction:

The data that will be explored was taken from Yahoo Finance through the 'quantmod()'
package. The objective of this research project, is to test whether the daily changes 
in price of an ETF are correlated with the change in volume during major events 
in financial crises. ETFs are 'basket' securities, which track benchmarks and 
industries, through the weighting of a collection of companies in that industry.

For this analysis, I pulled the 'SFY' ETF, which tracks the S&P 500 (500 largest 
companies in the US Stock Market), 'QQQ' which tracks Companies within the technology 
sector in the S&P, 'XLV' tracks the Health Care Sector, 'XLF' tracks Financial Sector, 
'XLE' tracks Energy Sector, and 'VNQ' (Tracks Real Estate Sector. 

Furthermore, the variables provided by the 'quantmod()' package, were Price, which
included price at market open, highest price in a trading day, lowest price in a 
trading day, and closing price, as well as Volume & adjusted price. Adjusted price 
will be used for plotting price changes through time, as it controls for dividends 
and any stock splits, which my delude the price of the ETF. Daily trading volatility 
will be calculated by the change in price in a day. 


## Relevant Visualizations:

```{r output = FALSE}
## loading in data and packages: 

library(quantmod)
library(lubridate)
library(tidyverse)

start <- ymd("2008-01-01")
end <- ymd("2026-05-01")


## getting symbols of the ETFs
getSymbols(c("SPY", "QQQ", "XLV", "XLF", "XLE", "VNQ"), src = "yahoo",
           from = start, to = end)

date_tib <- as_tibble(index(SPY)) |>
  rename(start_date = value)

qqq_tib <- as_tibble(QQQ)
spy_tib <- as_tibble(SPY)
xlv_tib <- as_tibble(XLV)
xlf_tib <- as_tibble(XLF)
xle_tib <- as_tibble(XLE)
vnq_tib <- as_tibble(VNQ)

all_stocks <- bind_cols(date_tib, qqq_tib, spy_tib, xlv_tib, xlf_tib, xle_tib, vnq_tib)


stocks_long <- all_stocks |>
  dplyr::select(start_date, SPY.Adjusted, QQQ.Adjusted, XLV.Adjusted, XLF.Adjusted,
                XLE.Adjusted, VNQ.Adjusted) |>
  pivot_longer(2:7, names_to = "Stock_Type", values_to = "Price") |>
  mutate(Stock_Type = fct_recode(Stock_Type,
                                 SYP = "SPY.Adjusted",
                                 QQQ = "QQQ.Adjusted",
                                 XLV = "XLV.Adjusted", 
                                 XLF = "XLF.Adjusted", 
                                 XLE = "XLE.Adjusted", 
                                 VNQ = "VNQ.Adjusted"
                                 ))

stocks_qqq <- stocks_long |> filter(Stock_Type == "QQQ")
stocks_spy <- stocks_long |> filter(Stock_Type == "SYP")
stocks_xlv <- stocks_long |> filter(Stock_Type == "XLV")
stocks_xlf <- stocks_long |> filter(Stock_Type == "XLF")
stocks_xle <- stocks_long |> filter(Stock_Type == "XLE")
stocks_vnq <- stocks_long |> filter(Stock_Type == "VNQ")
```

One of the key motivations for this project was going beyond price changes to 
isolate volatility in the markets. A key factor that moves markets are news and 
macroeconomic conditions. Thus, I want to show these market conditions and 
volatility across industries, not only in prices, but also in Volume traded. 

My expectation is that Volume will be strongly correlated with price, as volume 
is the mechanism that moves price (Supply and Demand), yet, what ultimatly is 
affected before price (hypothesis) is volume. Thus, the reason I make a distinction 
and want to statistically test, as well as visualize it. 

Since most volatility charts are shown through changes in price in the media and 
in intro to finance classes, the first visualization is the change in price. I have 
taken the time period from January 2008 to May 4th (deadline of this project), as
this time period lets us explore two financial crises; the 2008 financial crisis 
and the 2020 Covid-19 pandemic. 

```{r}
## looking at the Price of each ETF individually: 

ggplot(data = stocks_long, aes(x = start_date, y = Price)) +
  geom_line() +
  facet_wrap(~ Stock_Type) +
  theme_minimal() + 
  labs(title = "Changes in Price from 2008 to 2026",
       y = "Price (Adjusted)",
       x = "Date")


## comparing them through time: 

ggplot(data = stocks_long, aes(x = start_date, y = Price)) +
  geom_line(aes(colour = Stock_Type)) +
  geom_area(aes(fill = Stock_Type), alpha = 0.2, position = "identity") +
  theme_minimal() +
  scale_colour_viridis_d() +
  scale_fill_viridis_d() + 
  labs(title = "Changes in Price from 2008 to 2026",
       y = "Price (Adjusted)",
       x = "Date")
```

Looking only at price, the visual correlation between QQQ (tech within the S&P) 
and the S&P 500 is close. This can be explained, as about 40% of the weight within 
the S&P 500 is only tech stocks.


### Volatility meassures: 

```{r output = FALSE}
## cleaning data for volume: 

library(scales) ## for volume viz, makes y axis numbers, and not scientific 
## notation, source in appendix

stocks_volume <- all_stocks |>
  dplyr::select(start_date, QQQ.Volume, SPY.Volume, XLV.Volume, XLF.Volume,
                XLE.Volume, VNQ.Volume) |>
  pivot_longer(2:7, names_to = "Stock_Type", values_to = "Volume") |>
  mutate(Stock_Type = fct_recode(Stock_Type,
                                 QQQ = "QQQ.Volume",
                                 SPY = "SPY.Volume",
                                 XLV = "XLV.Volume", 
                                 XLF = "XLF.Volume", 
                                 XLE = "XLE.Volume", 
                                 VNQ = "VNQ.Volume"
                                 ))

vol_qqq <- stocks_volume |> filter(Stock_Type == "QQQ")
vol_spy <- stocks_volume |> filter(Stock_Type == "sandp")
vol_xlv <- stocks_volume |> filter(Stock_Type == "XLV")
vol_xlf <- stocks_volume |> filter(Stock_Type == "XLF")
vol_xle <- stocks_volume |> filter(Stock_Type == "XLE")
vol_vnq <- stocks_volume |> filter(Stock_Type == "VNQ")

stocks_rel <- stocks_volume |>
  filter(Stock_Type %in% c("QQQ", "SPY"))
```

```{r}
## overall volume

ggplot(data = stocks_volume, aes(x = start_date, y = Volume)) +
  geom_line() +
  facet_wrap(~ Stock_Type) +
  theme_minimal() + 
  scale_y_continuous(labels = label_number()) + 
    labs(title = "Changes in Volume from 2008 to 2026",
       y = "Volume",
       x = "Date")


## looking at all together: 

ggplot(data = stocks_volume, aes(x = start_date, y = Volume)) +
  geom_line(aes(colour = Stock_Type)) +
  geom_area(aes(fill = Stock_Type), alpha = 0.2, position = "identity") +
  theme_minimal() +
  scale_colour_viridis_d() +
  scale_fill_viridis_d() + 
  scale_y_continuous(labels = label_number()) + 
  labs(title = "Changes in Volume from 2008 to 2026",
       y = "Volume",
       x = "Date")


## looking at the relationship explained above

ggplot(data = stocks_rel, aes(x = start_date, y = Volume)) +
  geom_line(aes(colour = Stock_Type)) +
  geom_area(aes(fill = Stock_Type), alpha = 0.2, position = "identity") +
  theme_minimal() +
  scale_colour_viridis_d() +
  scale_fill_viridis_d() + 
  scale_y_continuous(labels = label_number()) +
  labs(title = "Changes in Volume in SPY vs. QQQ from 2008 to 2026",
       y = "Volume",
       x = "Date")
```

When looking at the volume, even as the y-axis scale changes from price to number 
of trades (definition of volume), the correlation is still there, although the 
gap between the two seems to be wider. There is much more volume traded with the 
S&P 500 than in QQQ. This could be due to the fact that less people own QQQ than 
the S&P 500, or that investors are more confident in keeping QQQ than S&P 500 as 
a whole, and are thus less responsive to market movements. 


### Looking at the Model (Correlation between Volatility & Volume)

```{r output = FALSE}
## making the data set for the general model: 
stocks_long <- 
  all_stocks |>
  pivot_longer(cols = -start_date,
               names_to = c("stock_type", ".value"),
               names_sep = "\\.")

## creating a log variable (dependent variable for the model)
## creating volatility in the difference between high and low
## creating return of the Adjusted price, adjusted minus last days price over the same

stocks_long <- stocks_long |> 
  group_by(stock_type) |> 
  mutate(log_volume = log(Volume), 
         volatility = High - Low, 
         stock_type = factor(stock_type)) 

## building the model: 
library(faraway)
library(broom)
library(GGally)
library(openintro)
library(tidyverse)
library(ggeffects)
library(pander)

mod <- lm(volatility ~ log_volume + stock_type + log_volume:stock_type,
               data = stocks_long)


mod_pred <- 
  ggpredict(mod, terms = c("log_volume [all]", 
                           "stock_type")) |> 
  as.data.frame(terms_to_colnames = TRUE) |> 
  as_tibble()
```

When building the model, we take the log version of volume, as it is a highly 
skewed variable, and we are trying to not violate model assumptions. 

```{r}
mod |> tidy() |> pander()

## mod viz 

ggplot(data = stocks_long, aes(x = log_volume, y = volatility)) +
  scale_colour_viridis_d() +
  geom_point(aes(colour = stock_type), alpha = 0.10) +
  geom_line(data = mod_pred, aes(x = log_volume, y = predicted), linewidth = 0.8) +
  facet_wrap(~ stock_type) +
  theme_minimal() +
  labs(y = "Daily Volatility In Price",
       x = "Trading Volume (log())",
       title = "How Trading Volume Predicts Daily Price Volatility")
```

Through the model output and the visualization, we can see that there is evidence 
of a positive linear relationship between daily volatility in price and trading 
volume. This supports the idea that volume can be used as an indicator for 
volatility in markets; the greater the volume, the more volatility there is in 
terms of price change per day. 

QQQ and SPY seem to have different behaviors compared to the other ETFs, which 
makes sense as the S&P 500 is highly responsive to the market, and QQQ is highly 
correlated to the S&P 500. 

Regarding the interaction term, I wanted to test of the effects of volume were 
different for each industry, which does seem to be the case. The higher the volume 
affects each industry differently. Our base group being QQQ, the coefficients 
are negative, which indicate that the effects are on average lower for the industries 
that aren't QQQ. 


### Visualizing Volume (2008 - 2011)

Now that we can take Volume as meassuremnt of volatility, I wanted to see if we 
plotted the changes in volume during financial crises, if we could identify key
market developments that would in turn change the price. Because these ETFs are 
high liquid, my expectation is that we will be able to identify these trends 
in the Volume traded, as we would be able to with price changes.  

```{r output = FALSE}
## looking at volume in 2008-2011

start_vol_08 <- ymd("2008-01-01")
end_vol_11 <- ymd("2011-01-01")

getSymbols(c("SPY", "QQQ", "XLV", "XLF", "XLE", "VNQ"), src = "yahoo",
           from = start_vol_08, to = end_vol_11)

date_tib_08 <- as_tibble(index(SPY)) |>
  rename(start_date = value)

qqq_tib_08 <- as_tibble(QQQ)
spy_tib_08 <- as_tibble(SPY)
xlv_tib_08 <- as_tibble(XLV)
xlf_tib_08 <- as_tibble(XLF)
xle_tib_08 <- as_tibble(XLE)
vnq_tib_08 <- as_tibble(VNQ)

all_stocks_08 <- bind_cols(date_tib_08, qqq_tib_08, spy_tib_08, xlv_tib_08, 
                           xlf_tib_08, xle_tib_08, vnq_tib_08)

stocks_volume_08 <- all_stocks_08 |>
  dplyr::select(start_date, QQQ.Volume, SPY.Volume, XLV.Volume, XLF.Volume,
                XLE.Volume, VNQ.Volume) |>
  pivot_longer(2:7, names_to = "Stock_Type", values_to = "Volume") |>
  mutate(Stock_Type = fct_recode(Stock_Type,
                                 QQQ = "QQQ.Volume",
                                 sandp = "SPY.Volume",
                                 XLV = "XLV.Volume", 
                                 XLF = "XLF.Volume", 
                                 XLE = "XLE.Volume", 
                                 VNQ = "VNQ.Volume"
                                 ))

vol_qqq_08 <- stocks_volume_08 |> filter(Stock_Type == "QQQ")
vol_spy_08 <- stocks_volume_08 |> filter(Stock_Type == "sandp")
vol_xlv_08 <- stocks_volume_08 |> filter(Stock_Type == "XLV")
vol_xlf_08 <- stocks_volume_08 |> filter(Stock_Type == "XLF")
vol_xle_08 <- stocks_volume_08 |> filter(Stock_Type == "XLE")
vol_vnq_08 <- stocks_volume_08 |> filter(Stock_Type == "VNQ")
```

```{r}
ggplot(data = stocks_volume_08, aes(x = start_date, y = Volume)) +
  geom_line(aes(colour = Stock_Type)) +
  geom_area(aes(fill = Stock_Type), alpha = 0.2, position = "identity") +
  theme_minimal() +
  scale_colour_viridis_d() +
  scale_fill_viridis_d() + 
  scale_y_continuous(labels = label_number()) + 
  labs(title = "Changes in Volume from 2008 to 2011",
       y = "Volume",
       x = "Date")

## looking at XLF (finance industry): 
ggplot(data = vol_xlf_08, aes(x = start_date, y = Volume)) + 
  geom_line() + 
  scale_y_continuous(labels = label_number()) + 
  geom_vline(xintercept = as.Date("2008-03-14"), linetype = "dashed", ## bear stearns
             colour = "red") + 
  geom_vline(xintercept = as.Date("2008-09-17"), linetype = "dashed", ## lehman brothers & AIG 
             colour = "blue") +
  labs(title = "Volume of XLF (Financial Sector) During the 2008 Crisis", 
       x = "Date", caption = "Dotted red line shows March 14th & Dotted blue line shows September 17th, 2008")

## looking at VNQ (real estate industry): 
ggplot(data = vol_vnq_08, aes(x = start_date, y = Volume)) + 
  geom_line() + 
  scale_y_continuous(labels = label_number()) + 
  geom_vline(xintercept = as.Date("2008-11-06"), linetype = "dashed", ## basis points & IMF 
             colour = "red") + 
  labs(title = "Volume of VNQ (Real Estate Sector) During the 2008 Crisis", 
       x = "Date", caption = "Dotted red line shows March 14th & Dotted blue line shows September 17th, 2008")
```

For the 2008 crisis, we can identify that the red line in the finance industry 
shows the collapse of Bear Stearns, one of the biggest Investment Banks to collapse, 
and the beginning of the 2008 financial crisis. The blue line shows the collapse 
of Lehman Brothers the Investment Bank, and AIG the insurance group that had backed 
the mortgages that started the financial crisis. 


### Visualizing Volume (2020 - 2023)

```{r output = FALSE}

## looking at volume in 2020-2023

start_vol_2020 <- ymd("2020-01-01")
end_vol_2023 <- ymd("2023-01-01")

getSymbols(c("SPY", "QQQ", "XLV", "XLF", "XLE", "VNQ"), src = "yahoo",
           from = start_vol_2020, to = end_vol_2023)

date_tib_20 <- as_tibble(index(SPY)) |>
  rename(start_date = value)

qqq_tib_20 <- as_tibble(QQQ)
spy_tib_20 <- as_tibble(SPY)
xlv_tib_20 <- as_tibble(XLV)
xlf_tib_20 <- as_tibble(XLF)
xle_tib_20 <- as_tibble(XLE)
vnq_tib_20 <- as_tibble(VNQ)

all_stocks_20 <- bind_cols(date_tib_20, qqq_tib_20, spy_tib_20, xlv_tib_20, 
                           xlf_tib_20, xle_tib_20, vnq_tib_20)

stocks_volume_20 <- all_stocks_20 |>
  dplyr::select(start_date, QQQ.Volume, SPY.Volume, XLV.Volume, XLF.Volume,
                XLE.Volume, VNQ.Volume) |>
  pivot_longer(2:7, names_to = "Stock_Type", values_to = "Volume") |>
  mutate(Stock_Type = fct_recode(Stock_Type,
                                 QQQ = "QQQ.Volume",
                                 sandp = "SPY.Volume",
                                 XLV = "XLV.Volume", 
                                 XLF = "XLF.Volume", 
                                 XLE = "XLE.Volume", 
                                 VNQ = "VNQ.Volume"
                                 ))

## for later: 

vol_qqq_20 <- stocks_volume_20 |> filter(Stock_Type == "QQQ")
vol_spy_20 <- stocks_volume_20 |> filter(Stock_Type == "sandp")
vol_xlv_20 <- stocks_volume_20 |> filter(Stock_Type == "XLV")
vol_xlf_20 <- stocks_volume_20 |> filter(Stock_Type == "XLF")
vol_xle_20 <- stocks_volume_20 |> filter(Stock_Type == "XLE")
vol_vnq_20 <- stocks_volume_20 |> filter(Stock_Type == "VNQ")
```

```{r}
## volume from 2020 - 2023

ggplot(data = stocks_volume_20, aes(x = start_date, y = Volume)) +
  geom_line(aes(colour = Stock_Type)) +
  geom_area(aes(fill = Stock_Type), alpha = 0.2, position = "identity") +
  theme_minimal() +
  scale_colour_viridis_d() +
  scale_fill_viridis_d() + 
  scale_y_continuous(labels = label_number())

## looking at S&P 500: 

ggplot(data = vol_spy_20, aes(x = start_date, y = Volume)) + 
  geom_line() + 
  scale_y_continuous(labels = label_number()) + 
  geom_vline(xintercept = as.Date("2020-03-13"), linetype = "dashed",
             colour = "red") + 
  labs(title = "Volume Change of S&P 500 During the Covid-19 Pandemic", 
       x = "Date", caption = "Dotted line shows March 13th, 2020")

## looking at health care: 

ggplot(data = vol_xlv_20, aes(x = start_date, y = Volume)) + 
  geom_line() + 
  scale_y_continuous(labels = label_number()) + 
  geom_vline(xintercept = as.Date("2020-03-13"), linetype = "dashed",
             colour = "red") + 
  geom_vline(xintercept = as.Date("2020-06-09"), linetype = "dashed", 
             colour = "blue") +
  geom_vline(xintercept = as.Date("2022-01-31"), linetype = "dashed", 
             colour = "green") + 
  labs(title = "Volume Change of XLV (HealthCare) During the Covid-19 Pandemic", 
       x = "Date", caption = "Red Dotted shows March 13th 2020, Blue Dotted shows June 9th 2020, 
       Green shows January 31st 2022")
```

Similarly, looking at the S&P 500, the red line shows the start of the pandemic 
which is the biggest change in volume. For the health care sector, the red line 
also depicts the start of the pandemic, the blue lines when the US surpassed 2 
million Covid Cases, and the green line signals a boost in the Omicron variant 
and the CDC requirement for people to get a 'boost' shot of the vaccine. 


### Visualizing Volume (2023 - Today)

```{r output = FALSE}
## looking at volume in 2023-today

start_vol_2023 <- ymd("2023-01-01")
end_vol_2026 <- ymd("2026-05-04")

getSymbols(c("SPY", "QQQ", "XLV", "XLF", "XLE", "VNQ"), src = "yahoo",
           from = start_vol_2023, to = end_vol_2026)

date_tib_today <- as_tibble(index(SPY)) |>
  rename(start_date = value)

qqq_tib_today <- as_tibble(QQQ)
spy_tib_today <- as_tibble(SPY)
xlv_tib_today <- as_tibble(XLV)
xlf_tib_today <- as_tibble(XLF)
xle_tib_today <- as_tibble(XLE)
vnq_tib_today <- as_tibble(VNQ)

all_stocks_today <- bind_cols(date_tib_today, qqq_tib_today, spy_tib_today, xlv_tib_today, 
                           xlf_tib_today, xle_tib_today, vnq_tib_today)

stocks_volume_today <- all_stocks_today |>
  dplyr::select(start_date, QQQ.Volume, SPY.Volume, XLV.Volume, XLF.Volume,
                XLE.Volume, VNQ.Volume) |>
  pivot_longer(2:7, names_to = "Stock_Type", values_to = "Volume") |>
  mutate(Stock_Type = fct_recode(Stock_Type,
                                 QQQ = "QQQ.Volume",
                                 sandp = "SPY.Volume",
                                 XLV = "XLV.Volume", 
                                 XLF = "XLF.Volume", 
                                 XLE = "XLE.Volume", 
                                 VNQ = "VNQ.Volume"
                                 ))

stocks_price_today <- all_stocks_today |>
  dplyr::select(start_date, QQQ.Adjusted, SPY.Adjusted, XLV.Adjusted, XLF.Adjusted,
                XLE.Adjusted, VNQ.Adjusted) |>
  pivot_longer(2:7, names_to = "Stock_Type", values_to = "Price") |>
  mutate(Stock_Type = fct_recode(Stock_Type,
                                 QQQ = "QQQ.Adjusted",
                                 sandp = "SPY.Adjusted",
                                 XLV = "XLV.Adjusted", 
                                 XLF = "XLF.Adjusted", 
                                 XLE = "XLE.Adjusted", 
                                 VNQ = "VNQ.Adjusted"
                                 ))


## COME BACK TOO WHAT DO I NEEDDD

vol_qqq_today <- stocks_volume_today |> filter(Stock_Type == "QQQ")
vol_spy_today <- stocks_volume_today |> filter(Stock_Type == "sandp")
vol_xlv_today <- stocks_volume_today |> filter(Stock_Type == "XLV")
vol_xlf_today <- stocks_volume_today |> filter(Stock_Type == "XLF")
vol_xle_today <- stocks_volume_today |> filter(Stock_Type == "XLE")
vol_vnq_today <- stocks_volume_today |> filter(Stock_Type == "VNQ")
```

```{r}
## volume from 2023 - today

ggplot(data = stocks_volume_today, aes(x = start_date, y = Volume)) +
  geom_line(aes(colour = Stock_Type)) +
  geom_area(aes(fill = Stock_Type), alpha = 0.2, position = "identity") +
  theme_minimal() +
  scale_colour_viridis_d() +
  scale_fill_viridis_d() + 
  scale_y_continuous(labels = label_number())

## price from 2023- today: 

ggplot(data = stocks_price_today, aes(x = start_date, y = Price)) +
  geom_line(aes(colour = Stock_Type)) +
  geom_area(aes(fill = Stock_Type), alpha = 0.2, position = "identity") +
  theme_minimal() +
  scale_colour_viridis_d() +
  scale_fill_viridis_d() + 
  scale_y_continuous(labels = scales::comma)


## looking at S&P 500: 

ggplot(data = vol_spy_today, aes(x = start_date, y = Volume)) + 
  geom_line() + 
  scale_y_continuous(labels = label_number()) + 
  geom_vline(xintercept = as.Date("2025-04-02"), linetype = "dashed", ## liberation day
             colour = "red") + 
  labs(title = "Volume Change of S&P 500 from 2023 - Today", 
       x = "Date", caption = "Dotted line shows April 2nd, 2025")


## looking at QQQ: 

ggplot(data = vol_qqq_today, aes(x = start_date, y = Volume)) + 
  geom_line() + 
  scale_y_continuous(labels = label_number()) + 
  geom_vline(xintercept = as.Date("2025-04-02"), linetype = "dashed", ## liberation day
             colour = "red") + 
  labs(title = "Volume Change of QQQ from 2023 - Today", 
       x = "Date", caption = "Dotted line shows April 2nd, 2025")
```

We can see liberation day through volume in both of the dotted lines. This is the
most significant macro event in the past 3 years according to volume. Not even 
the war in Iran or other Middle Eastern conflicts have created more volatility 
in equity markets. 


## Conclusion: 

Volume is a powerful variable that can help predict and evaluate volatility in 
markets, especially with the Technology sector and the S&P 500. We can see the 
correlation through the model, and its immediate response to macroeconomic events. 

In the future, it would be interesting to see the difference in volume and its 
impact on price, on macro news vs. a change in monetary and fiscal policy. All 
the spices that I point out are major shocks to markets that are 'macro' events, 
but a lot of these lower spikes are related to interest rates. 


## Appendix: 

  * Blog Post Link: https://asantanalugo.github.io/ds334_blog/
  * GitHub Repository: https://github.com/asantanalugo/finalproject
  * For adjusting the Y-axis from scientific notation, I asked Gemini: 
    * Prompt: How can I make the Y-Axis of my plot go from Scientific notation 
    to normal numbers in R using the scale_y_continuous I used in class?
    * Response: Transitioning from scientific notation to "normal" numbers in 
    ggplot2 is a common hurdle. By default, R switches to scientific notation 
    once numbers get sufficiently large or small to keep the labels from 
    overlapping. To fix this within scale_y_continuous, you’ll want to use the 
    labels argument combined with the scales package.
    The Quick Fix The most straightforward way is to use scales::label_comma() 
    (for commas) or scales::label_number() (for plain numbers).
